### 2020-04-15 dataclean.tex
Cleaning up.
fixed section refs

\section{Viewing and Cleaning the Data}
\label{sec:clean}
\fix{George's section: The two views of GPU life: by SN and by
  location, its use in cleaning data, etc.}

As we need to recover durations from this data, correct processing
involves time adjustments for switching between daylight saving time
and standard time. We perform this by setting a reference time zone
(Eastern time) and converting all date-times from strings into
date-time variables \fix{(is there a name for this?)} with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic.

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Viewing and Cleaning the Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Viewing and Cleaning the Data}
\label{section:dataclean}
As we need to recover durations from this data, correct processing
involves time adjustments for switching between daylight saving time
and standard time. We perform this by setting a reference time zone
(Eastern time) and converting all date-times from strings into
date-time variables \fix{(is there a name for this?)} with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic.

### 2020-04-15 intro.tex
fixed section refs

We begin by describing related work in Sec.~\ref{sec:related}. Our
data collection is desctibed in Sec.~\ref{sec:dataprep} and the data
cleaning, checking, and lifetime summarization process in
Sec.~\ref{sec:dataclean}. A timme between failures analysis is given
in Sec.~\ref{sec:tbf}. Survival analysis based on Kaplan-Meier
modeling and Cox regression modeling of relative hazard rates are in
Sec.~\ref{sec:survival}. Finally, we discuss our main conclusions and
recommendations in Sec.~\ref{sec:discussion}.

>>>>

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the data
cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A timme between failures analysis is given
in Sec.~\ref{section:tbf}. Survival analysis based on Kaplan-Meier
modeling and Cox regression modeling of relative hazard rates are in
Sec.~\ref{section:survival}. Finally, we discuss our main conclusions and
recommendations in Sec.~\ref{section:discussion}.
